### 2020-11-02 doc/manuscript/Dow_manuscript.Rmd
Closes #8

•	Bayesian heirarchal model
This mixed-effect model was run within a heirarchal bayesian framework.

>>>>

•	Bayesian heirarchical model
This mixed-effect model was run within a hierarchical Bayesian framework and fit using the `rstanarm` R interface to the Stan programming language @rstanarm_2020. In all cases unless otherwise specified, all prior distributions are set to be the weakly informative defaults. 
<!--
TODO added by Bert: Whereever we specify model details, include details about prior from here:
https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html#default-weakly-informative-prior-distributions
-->
